\section{Three-Granularity Edge Predictor}
\label{sec:predictor}

For routing to be deployable, the gating decision must be made
\emph{before} any expensive model has run. We train a lightweight
classifier to predict, from features computable at the VADER stage
alone, whether a sentence will produce high committee disagreement
(binary target: $\mathrm{SDI}_{\max}>0.7$). The feature engineering
mirrors the committee's own granularity stratification ---
word, phrase, and sentence --- and we report the marginal
contribution of each.

\paragraph{Word-level.}
6 VADER outputs (positive/negative/neutral fractions, compound,
confidence, $|$compound$|$) and 6 surface indicators (number,
currency, contrast word, negation, length). We mine \emph{unigram}
triggers via log-odds + $z$-score on the high-SDI subset; top words
include \texttt{decreased}, \texttt{dropped}, \texttt{fell}.

\paragraph{Phrase-level.}
We extend the log-odds miner to $n\!\in\!\{2,3\}$ and use the
top-30 bigram / trigram triggers as binary presence features.
Bigrams capture phrase-bound polarity that single words miss
(\texttt{down\_from}, \texttt{compared\_profit}, and ideally
context-flipping pairs like \texttt{loss\_narrowed} vs.\
\texttt{loss\_widened}). On FPB the bigram lift is small ($+0.01$
AUC over unigram), but the running example
(Section~\ref{sec:intro}) shows the linguistic mechanism is real.

\paragraph{Sentence-level.}
We encode each sentence with the multilingual MiniLM-L12 model
(22\,M params, $\approx$10\,ms/sentence on CPU) and PCA-reduce the
384-dim embedding to 16 components. The same module powers the SCD
(Section~\ref{sec:framework:scd}) and the cross-lingual pilot
(Section~\ref{sec:experiments:zh}).

Table~\ref{tab:predictor} reports the seven-variant ablation. Word
features alone reach AUC $=0.69$; phrase adds $+0.01$;
\emph{sentence} adds $+0.04$ --- the largest single-granularity
contribution. XGBoost over the full feature set reaches AUC $=0.85$.
A non-deployable upper bound that encodes the LLM's R1 reasoning
text reaches AUC $=0.94$, marking remaining headroom for deployable
variants.

\begin{table*}[t]
\centering
\small
\caption{Edge predictor ablation across the three feature
granularities. AUC-PR = area under precision-recall;
P@R$x$ = precision at $x$\,\% recall; P@top10 = precision among the
10\,\% riskiest predictions. Sentence-BERT features add the largest
single-granularity lift. The non-deployable upper bound encodes the
LLM's R1 explanation text and is not counted toward the deployable
ceiling.}
\label{tab:predictor}
\begin{tabular}{lrrrrr}
\toprule
Model & AUC-ROC & AUC-PR & P@R20 & P@R50 & P@top10 \\
\midrule
random              & 0.503 & 0.328 & 0.353 & 0.332 & 0.351 \\
LR-unigram          & 0.694 & 0.566 & 0.788 & 0.479 & 0.773 \\
LR-uni+bigram       & 0.697 & 0.570 & 0.764 & 0.486 & 0.742 \\
LR-uni+bi+trigram   & 0.703 & 0.582 & 0.808 & 0.503 & 0.773 \\
LR-sentence-only    & 0.688 & 0.583 & 0.944 & 0.472 & 0.814 \\
\textbf{LR-uni+bi+sent.} & \textbf{0.741} & \textbf{0.607} & 0.768 & 0.554 & 0.742 \\
\textbf{XGBoost (all)}   & \textbf{0.848} & \textbf{0.745} & \textbf{0.943} & \textbf{0.759} & \textbf{0.866} \\
\midrule
XGBoost+reasoning$^\dagger$ & 0.937 & 0.897 & 0.990 & 0.964 & 0.990 \\
\bottomrule
\end{tabular}
\\[2pt]
\footnotesize $^\dagger$Encodes the LLM's R1 explanation text
(non-deployable upper bound).
\end{table*}
