\section{Discussion and Deployment}
\label{sec:discussion}

\paragraph{Distributed deployment at scale.}
Each tier of TriAgent is stateless and shardable. At 10\,M users
($\sim$1\,B queries/day): L1 (VADER) is CPU-co-located with the API
gateway ($\sim$30\,K queries/sec/core); L2 (FinBERT) is a stateless
GPU service at $\approx$5\,K queries/sec per A5000-class card,
needing 3--4 instances; L3 (Qwen-$N$) handles only 5--15\,\% of
nominal traffic after the SDI gate ($\sim$15\,\% trigger) and SCD
cache (10--55\,\% absorbed depending on $\tau$), giving roughly
\textbf{18 GPUs at the 10\,M-user scale vs.\ $\sim$3{,}000 for an
always-L3 deployment}. The SCD is the only stateful component ---
materialised as a single FAISS index~\cite{johnson2019faiss} per
region with asynchronous replication; a 1\,M-entry cache occupies
$\approx$1.5\,GB RAM and serves cosine queries in microseconds.

\paragraph{Customer-language regime.}
On Twitter Financial News (TFNS~\cite{tfns}, $\sim$12\,K customer-
style tweets) FinBERT collapses from $F_1=0.88$ to $0.66$
($-22$\,pp), while Qwen-7B holds at $0.76$. This inverts the
``specialist beats LLM'' relationship for fragmented text and
explains why the critic protocol regresses on TFNS: with weak V$+$F
scaffolding, a critic underperforms the LLM alone. The SDI gate
handles this by accepting a per-domain trigger threshold.

\paragraph{Cross-family scaling is not universal.}
The critic plateau holds within Qwen2.5-Instruct (1.5\,B--7\,B) but
does not transfer cleanly: critic@Mistral-7B reaches only $F_1=0.79$.
Debate is more family-robust (debate@Mistral-7B$=0.82$). A
practitioner should run the cheap persona-vote sanity check before
committing to a specific LLM family for the L3 tier.

\paragraph{Honest limitations.}
The 20-ticker back-test uses FPB sentences as a controlled news
proxy; we do not claim it predicts real markets. The adversarial
detector AUC drops to $\approx\!0.5$ for synonym / numeric / typo
attacks --- a perturbation-specific defence is the most pressing
follow-on. The Chinese pilot shows that the V$+$F lexicon$+$
specialist tier needs Chinese-specific replacements for full
deployment.
