% TriAgent — FinLLM @ IJCAI 2026 submission
% Compile:  pdflatex main && bibtex main && pdflatex main && pdflatex main
% Self-contained: ijcai26.sty + named.bst + figures/*.pdf + sections/*.tex
% all in this directory.

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in

\usepackage{ijcai26}

\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[switch]{lineno}

% Line numbers disabled (FinLLM/IJCAI 2026 submission does not require lineno)
% \linenumbers

\urlstyle{same}

\graphicspath{{figures/}}

\pdfinfo{
/TemplateVersion (IJCAI.2026.0)
}

\title{TriAgent: Divergence-Aware Multi-Agent Committees for
       Cost-Efficient and Privacy-Preserving Financial Sentiment Analysis}

\author{
Isabel Xu$^{1,*}$
\and
Cynthia Xu$^{1,*}$\and
Rachel Ren$^2$\and
Cong Guo$^3$\and
Jiacheng Ding$^{3,\dagger}$\\
\affiliations
$^1$The Overlake School\\
$^2$Edwards Vacuum Inc.\\
$^3$The University of Memphis\\
\emails
\{xushuyao, xuningshu\}@gmail.com,
rachelren@gmail.com,
\{cguo, jding2\}@memphis.edu\\
$^*$Equal contribution. \quad $^\dagger$Corresponding author.
}

\begin{document}
\maketitle

\begin{abstract}
Production deployments of LLM-based financial sentiment analysis face
a structural cost problem: most queries are trivially classifiable yet
are routinely processed by expensive cloud reasoners, and the bill
scales linearly with user count.
We present \textbf{TriAgent}, a divergence-aware multi-agent committee
that stacks three increasingly contextual tiers --- a word-level
lexicon agent (VADER), a sentence-level domain transformer (FinBERT),
and a cross-sentence reasoner (Qwen2.5-Instruct, swept from 0.5\,B to
14\,B-4bit and across families) --- and routes queries by a three-way
\emph{Semantic Divergence Index} (SDI). On Financial PhraseBank we
find: (i) the domain specialist alone (F1$=$0.88) outperforms every
generic LLM up to 7\,B (F1$=$0.81) at $60\times$ lower cost; (ii) when
the LLM is re-tasked as a \emph{critic} over the smaller agents'
outputs, F1 plateaus at $\approx$0.87 across model sizes from 1.5\,B
to 7\,B --- ``\emph{interaction substitutes for parameters}'' --- but
this plateau is granularity-stratified, not multi-agent-per-se: a
3-persona Qwen-1.5B vote drops to F1$=$0.66; (iii) a Shared Consensus
Dictionary (SCD) using multilingual sentence-BERT serves as a
cross-lingual canonicalizer, answering 95\% of Chinese queries from an
English cache at F1$=$0.99; (iv) the same SDI signal that gates
routing doubles as a post-hoc LLM-hallucination detector at AUC$=$0.90.
A 20-ticker backtest shows the SDI two-stage strategy attains the best
risk-adjusted return (Sharpe$=$3.50) among all evaluated strategies,
and a scale analysis shows TriAgent saves \$9.3\,M/year vs. the
default-to-cloud-LLM baseline at 10\,M users. The framework is
fully open-source and edge-deployable on a single 24\,GB GPU.
\end{abstract}

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_framework}
\input{sections/04_mining_and_predictor}
\input{sections/05_experiments}
\input{sections/06_security_and_bias}
\input{sections/07_discussion}
\input{sections/08_conclusion}

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
